Safe Shared Memory for Concurrent Algol

### 2017-10-11 proposal.tex
...
add a draft abstract

\begin{abstract}
  [Please put some abstract material here.]
\end{abstract}

@@

Farzaneh will write some general amterial here.

>>>>

\begin{abstract}
  Establishing safety properties for code that mixes concurrency with
  (shared) memory is notoriously difficult; the experience of the past
  several years suggests that restricted languages can provide a
  suitable means to achieve general safety results without sacrificing
  performance. Languages like \Lang{Rust} and \Lang{Go} are a step in
  the right direction, but are not currently backed by a precise
  semantics; we will attempt to thoroughly develop the theory and
  practice of a small Algol-family language featuring concurrency and
  shared memory, establishing several crucial safety properties at the
  language level.
\end{abstract}

@@

Farzaneh will write some general material here.
